this is for the result part of the draft

### 2017-04-03 analysis/draft.Rmd
Files commited by wflow_commit.

    plot_f = ggplot(f_dat,aes(x = variable,y = Factor,fill = factor(variable))) +
      geom_bar(stat = "identity",width = 0.5,color = "black") +
      scale_fill_manual(values=color.fill) + theme(legend.position="none") +
      labs(title = paste("factor",k,"with PVE=",round(pve,3)), y = y_lab ,x = "index")
  }else{
    f_dat <- data.frame(variable = 1:P, Factor = f,
                      sign.f = factor(sign(f)),
                      variablenames = f_lables,
                      hjust = factor(sign(f)))

@@

    plot_f = ggplot(f_dat,aes(x = factor(variable),y = Factor,fill = factor(variable))) +
      geom_bar(stat = "identity",width = 0.5,color = "black") +
      scale_fill_manual(values=color.fill) + theme(legend.position="none") +
      geom_text(size = 2.75,angle = 90,hjust = as.character(f_dat$hjust),
                nudge_y = sign(f_dat$Factor) * 0.1 * mean(abs(f_dat$Factor)) ) +
      ylim(lower_f,upper_f) +
      labs(title = paste("factor",k,"with PVE=",round(pve,3) ), y = y_lab,x = "index")
  }
  return(plot_f)
}
load("../data/GTExdata/bflashvarcol.rds")
load("../data/GTExdata/gtexEQTL_zscore.rds")
plot.factor(Y = t(zscore),g = b_flash,k = 1,loading_label = FALSE,color.fill = as.character(colordata[,2]))

@@

# ggplot(f_dat,aes(x = factor(variable),y = Factor,fill = factor(variable))) +
#       geom_bar(stat = "identity",width = 0.5,color = "black") +
#       scale_fill_manual(values=color.fill) + theme(legend.position="none")

>>>>

    plot_f = ggplot(f_dat,aes(x = variable,y = Factor,fill = factor(variable),color = factor(variable))) +
      geom_bar(stat = "identity",width = 0.6) +scale_color_manual(values=color.fill)+
      scale_fill_manual(values=color.fill) + theme_grey()+ theme(legend.position="none",plot.background = element_rect()) + 
      labs(title = paste("factor",k,"with PVE=",max(0.001,round(pve,3))), y = y_lab ,x = "index",color = "index",fill="index")
  }else{
    f_dat <- data.frame(variable = 1:P, Factor = f,
                      sign.f = factor(sign(f)),
                      variablenames = f_lables,
                      hjust = factor(sign(f)))

@@

    plot_f = ggplot(f_dat,aes(x = variable,y = Factor,fill = factor(variable),color = factor(variable))) +
      geom_bar(stat = "identity",width = 0.6) +scale_color_manual(values=color.fill)+
      scale_fill_manual(values=color.fill) + theme_grey()+ theme(legend.position="none",plot.background = element_rect())  +
      geom_text(size = 2.75,angle = 90,hjust = as.character(f_dat$hjust),
                nudge_y = sign(f_dat$Factor) * 0.1 * mean(abs(f_dat$Factor)) ) +
      ylim(lower_f,upper_f) +
      labs(title = paste("factor",k,"with PVE=",max(0.001,round(pve,3)) ), y = y_lab,x = "index")
  }
  return(plot_f)
}
load("../data/GTExdata/bflashvarcol.rds")
load("../data/GTExdata/gtexEQTL_zscore.rds")
# plot.factor(Y = t(zscore),g = b_flash,k = 1,loading_label = FALSE,color.fill = as.character(colordata[,2]))

@@

# ggplot(f_dat,aes(x = factor(variable),y = Factor,fill = factor(variable))) +
#       geom_bar(stat = "identity",width = 0.5,color = "black") +
#       scale_fill_manual(values=color.fill) + theme(legend.position="none")
pic = list()
for(i in 1:26){
  pic[[i]] = plot.factor(Y = t(zscore),g = b_flash,k = i,
                         loading_label = FALSE,color.fill = as.character(colordata[,2]))$plot_l
}

library(cowplot)
plot_grid(pic[[1]], pic[[2]],pic[[3]],
          pic[[4]],pic[[5]],pic[[6]],
          pic[[7]],pic[[8]],pic[[9]],
          labels = c("","","","","","","","",""), ncol = 3)

plot_grid(pic[[10]], pic[[11]],pic[[12]],
          pic[[13]],pic[[14]],pic[[15]],
          pic[[16]],pic[[17]],pic[[18]],
          labels = c("","","","","","","","",""), ncol = 3)
plot_grid(pic[[19]], pic[[20]],pic[[21]],
          pic[[22]],pic[[23]],pic[[24]],
          pic[[25]],pic[[26]],
          labels = c("","","","","","","","",""), ncol = 3)
line1 = plot_grid(pic[[19]], pic[[20]],pic[[21]],
          labels = c("","",""), ncol = 3)
line2 = plot_grid(pic[[22]],pic[[23]],pic[[24]],
          labels = c("","",""), ncol = 3)
pic_26 =  pic[[26]] + theme(legend.direction = "horizontal",legend.position = "right")+guides(col = guide_legend(ncol = 8))
line3 = plot_grid(pic[[25]],pic_26,
          labels = c("",""), ncol = 2,rel_widths = c(1, 2))

plot_grid(line1,line2,line3,labels = c("","",""), ncol = 1)
# need one for the lengend
